Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-11-08 paper/main.tex
adding confusing non-sense

The T-web shows alignment/anti-alignment trends starting at masses of
$10^{10}$\hMsun, two orders of magnitude less than the V-web. In this
case we see an alignment along the first and third eigenvectors. It
means that halos in filamentary environments tend to be aligned with
the filament, while halos in pancake environments are perpendicular to
the sheet.

>>>>

The T-web shows alignment  trends starting at masses of
$10^{10}$\hMsun, two orders of magnitude less than the V-web. In this
case we see an alignment along the first and third eigenvectors. It
means that halos in filamentary environments tend to be aligned with
the filament, while halos in pancake environments are perpendicular to
the sheet.

The most massive halos showing the strongets alignment trends are not
usually located in regions classified as peaks where all the
eigenvectors are are positive, meaning that thre is
collapse/compressive stress in all directions.

In this situation we
can interpret alignment both along the first and third eigenvector as
a signature that most massive halos tend to be aligned midway between
the first and second eigenvector, lying along the plane defined by the
second eigenvector.
